Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-07 inc/photocathode/single_photon/single_photon.tex
more work on single_photon photoemission

@@

>>>>

Single-photon photoemission is the most common photoemission process and the easiest to explain.
As described by Einstein in his famous paper on ``the photoelectric effect,'' if an electron absorbs a photon whose energy is sufficient to promote the electron above the local vacuum level, it become free to leave the host material.
In Section \ref{sec:must_reduce_transverse_momentum}, we have already seen that flat metal photocathodes employing single-photon photoemission are not likely to be useful for UEM since the transverse momentum variance $\Delta p_{\smallT} = \sqrt{ m \Delta E / 3 } $ \cite{dowell_quantum_2009} cannot be reduced without also reducing the emission efficiency which is proportional to $\Delta E^2$ \cite{shalaev_electron_1994}.

@@

An example of single-photon photoemission is presented in \ref{fig:single_photon_tungsten}, wherein a sample of polished tungsten (W), having a work function $\Phi \approx $ 4.55 eV, %TODO ref
is used as a photocathode.
When paired with our $\hbar \omega = $ 4.75 eV photon energy laser (see Section \ref{sec:laser}) the excess photoemission energy $\Delta E = \hbar \omega - \Phi \approx $ 0.2 eV.
